R Notebook

### 2021-03-10 eda.Rmd
EDA on region

```{r}
streetrx <- streetrx %>% filter(state != 'USA')
```

>>>>

```{r}
streetrx <- streetrx %>% filter(state != 'USA') %>% droplevels()
```

## USA region

```{r}
table(streetrx$USA_region)
```

Let's visualize the estimated density for these 4 groups. For visualization purposes, we omit ppm greater than 10 (which is largely the entire data anyawy)

```{r}
small_ppm <- streetrx %>% filter(ppm < 10)
ggplot(small_ppm, aes(x=ppm, color=USA_region)) + geom_density(bw=0.5)
```

They all look pretty similar actually *except* for South, which seems to be higher priced than the other on average
